% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Wesley Brooks}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={7in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

%Use bullets for reference list
\makeatletter
\renewcommand\@biblabel[1]{\textbullet}
\makeatother

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://www.stat.wisc.edu/}{University of Wisconsin-Madison} \\
  Department of Statistics \\
  Medical Sciences Center \\
  Madison, WI 53706
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (608) 561-2172 \\
    Email: & \href{mailto:wrbrooks@uwalumni.com}{\tt wrbrooks@uwalumni.com} \\
    Homepage: & \href{http://somesquares.org}{\tt http://somesquares.org} \\
  \end{tabular}
\end{minipage}

I'm a number-crunching bicyclist gardener Alaskan sailor who's ABD in Wisconsin and looking to return to the Pacific Northwest.

I care about technology, the environment, human welfare and happiness (the order changes daily!) My current research focus is nonparametric spatial statistics and local modeling - for instance: what factors are predictors of the poverty rate for a given county in the state of Wisconsin, and are those factors different from other parts of the state and country?

Statistics is special because of its focus on inference and observation. How do we know that we know what we know? That's statistics. Also: what do we not know? And which is more important to predicting the consequences of our actions?

I'm passionate about reproducible research, design, and communicating effectively through visualizations.

\section*{Education}

\begin{itemize}
    \item Ph.D. Statistics, University of Wisconsin-Madison, 2015.
    \item M.S. Statistics, University of Wisconsin-Madison, 2011.
    \item B.S. Electrical Engineering \& Math, University of Alaska-Fairbanks, 2007.
\end{itemize}


\section*{Employment}

\begin{itemize}
\item U.S. Geological Survey. Middleton, WI. Graduate Research Assistant. 2010-present.
\item University of Wisconsin-Madison. Madison, WI. Graduate Student. 2009-present.
\item Boreal Controls. Juneau, AK. Electical Engineer-in-Training. 2003-2009.
\end{itemize}


\subsection*{Journal Articles}

    \bibliography{articles}
    \bibliographystyle{plain}

\subsection*{Presentations}

    \bibliography{presentations}
    \bibliographystyle{plain}

\begin{itemize}
\item  Modern Statistical Methods for Predicting Bacterial Exceedances in  
   Beach Water; \emph{American Water Resources Association, Wisconsin Chapter}; March 3-4, 2011.

\item Web-Based Tools to Expand Access to Beach Water Quality Monitoring. \emph{Great Lakes Beaches Conference}; October 18 2010.
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\nocite{*}
\end{document}
